
How can we quantitatively describe developmental growth at scale? Meta-analysis is one promising method. In this paper, we presented a bird-eye view of developmental psychology by synthesizing 23 meta-analyses available on MetaLab. We found great diversity in the shapes of the best-fitting models for each domain – while some phenomena showed larger and larger effects with development, quite a number of others stayed constant, suggesting a distinction between small but measurable in-lab effects and behaviors that can easily be observed in individual children (effect sizes > 2). We also considered the moderating effects of different methodological factors, including the type of behavioral measure, the type of stimuli exposure methods, stimuli naturalness, and whether the work is done by a “major author”. These factors moderate effect sizes from different domains in heterogeneous ways, though we did find evidence for naturalistic stimuli leading to larger effects in a number of research areas. 


```{r 2-col-imageb, fig.env = "figure*", fig.pos = "h!", fig.width=7, fig.height=5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Predictions of the best-fitting functional forms of the age model. X-axis is age in months. Y-axis is the predicted effect size. For each research area, we plotted the predicted values for the age range included in the dataset."}

age_range_df <- d %>% 
  group_by(ds_clean) %>% 
  summarise(min_age = min(mean_age_months, na.rm = TRUE), 
            max_age = max(mean_age_months, na.rm = TRUE)) %>% 
  rename(ds_name = ds_clean)


categorized_age_pred_df <- all_age_pred %>% 
  select(pred, ds_name, ci.lb, ci.ub) %>% 
  group_by(ds_name) %>% 
  mutate(mean_age_months = (row_number() + 1) / 2) %>% 
  left_join(age_range_df, by = c("ds_name")) %>% 
  filter(mean_age_months > min_age, 
         mean_age_months < min(36, max_age))%>% 
  mutate(
    ds_type = case_when(
      ds_name %in% c( "Language discrimination and preference", 
                     "Mispronunciation sensitivity", 
                     "Natural speech preference", "Sound symbolism", "Statistical sound category learning (habituation)", 
                     "Vowel discrimination (native)",
                     "Vowel discrimination (non-native)" ,"Word Segmentation (combined)",
                     "Statistical word segmentation") ~ "Sounds", 
      
      ds_name %in% c("Familiar word recognition", 
                     "Cross-situational word learning", 
                      "Label advantage in concept learning",
                     "Mutual exclusivity",
                     "Online word recognition",
                     "Syntactic bootstrapping",
                     "Switch task") ~ "Words",
      
      ds_name %in% c("Gaze following (combined)",
                     "Prosocial agents",
                     "Symbolic play", 
                     "Infant directed speech preference") ~ "Communication", 
      
      ds_name %in% c("Abstract rule learning",  
                     "Categorization bias", 
                     "Simple arithmetic competences") ~ "Cognitive abilities"
     )
  ) %>% 
  mutate(pred = case_when(
    ds_name == "Abstract rule learning" ~ -pred, 
    ds_name == "Switch task" ~ -pred,
    ds_name == "Statistical word segmentation" ~ -pred,
    TRUE ~ pred
  )) %>% 
  mutate(
    ci.lb = case_when(
      ds_name %in% c("Abstract rule learning", "Switch task", "Statistical word segmentation") ~ -ci.lb,
      TRUE ~ ci.lb
    ), 
    ci.ub = case_when(
      ds_name %in% c("Abstract rule learning", "Switch task", "Statistical word segmentation") ~ -ci.ub,
      TRUE ~ ci.ub
    )
  ) %>% 
  select(ds_name, ds_type, mean_age_months, pred, ci.lb, ci.ub) %>% 
  mutate(ds_name = case_when(
    ds_name == "Word Segmentation (combined)" ~ "Word segmentation", 
    ds_name == "Statistical sound category learning (habituation)" ~ "Statistical sound category learning", 
    ds_name == "Simple arithmetic competences"~ "Simple arithmetic competence",
    TRUE ~ ds_name
  ))



label_df <- categorized_age_pred_df %>% 
  filter(mean_age_months == max(mean_age_months)) 

label_df$x = c(
  15 - 3, 
  29.5 + 11, #"Vowel discrimination (native)"
  17.5 - 5, #"Vowel discrimination (non-native)"
  18.5, #"Statistical word segmentation"
  30 + 2, #"Online word recognition"
  35.5 + 4, #Mutual exclusivity , 
  35.5 + 8, #Sound symbolism, 
  35.5 + 5 , # Categorization bias
  15 + 3,#Familiar word recognition
  13 + 4,#Abstract rule learning
  24.5+ 3, #Switch task,
  35.5 + 4,#"Mispronunciation sensitivity"
  31.5 + 8, #Prosocial Agents
  9 + 4, #"Simple arithmetic competences"
  35.5 + 5,#Symbolic play
  12.5 , #"Natural speech preference"
  35.5 + 3, # "Cross-situational word learning"
  11.5 + 8, # "Language discrimination and preference"
  35.5 + 5, # "Syntactic bootstrapping"
  11 + 5, #"Statistical sound category learning (habituation)"
  23.5 + 4, #"Gaze following (combined)"
  24.5 + 14, #"Word Segmentation (combined)"
   18.5# "Infant directed speech preference"
  
)
label_df$y = c(
  0.05004268 - 0.5, 
  0.5901183 + 0.2, #"Vowel discrimination (native)"
  0.6457766 + 1, #"Vowel discrimination (non-native)"
  -0.07808538 - 0.2, #"Statistical word segmentation"
  2.964331 + 0.5, #"Online word recognition"
  1.44 + 0.3,#Mutual exclusivity
  0.383, #Sound symbolism, 
  0.275 + .4, # Categorization bias
  0.805 + 0.3,#Familiar word recognition
  0.05 - 0.5 ,#Abstract rule learning
  0.156 - 0.3,#Switch task
  1.62 + 0.5,#"Mispronunciation sensitivity"
  0.405, #Prosocial agents
  0.249 + 0.6,#"Simple arithmetic competences"
 0.627 + 0.5, #Symbolic play
  0.811 + 1.3, #"Natural speech preference"
  0.545 + .3, # "Cross-situational word learning"
  0.265 - 1, # "Language discrimination and preference"
  0.103 - 0.5, # "Syntactic bootstrapping"
  0.557 + 0.5, #"Statistical sound category learning (habituation)"
  2.99 + 0.3, #"Gaze following (combined)"
 0.2 + 1.2, #"Word Segmentation (combined)"
 0.467 - 0.6# "Infant directed speech preference"
  
)



p <- categorized_age_pred_df %>% 
  ggplot(aes(x = mean_age_months, y = pred, group = ds_name, col = ds_name)) + 
  geom_hline(yintercept = 0, linetype = "dashed", alpha = .5) + 
  geom_line(alpha = 1, width = 2)+ 
  geom_ribbon(
              aes(x = mean_age_months, y = pred, ymin = ci.lb, ymax = ci.ub, fill = ds_name), alpha = 0.1, colour = NA)+ 
  geom_text(data = label_df, aes(x = x, y = y, label = ds_name, size = 0.2), 
                   size = 2.2,
                  segment.color = NA) + 
  xlim(0, 48) + 
  ylim(-1.5, 4) + 
  facet_wrap(~factor(ds_type, levels = c("Sounds", "Words", "Communication", "Cognitive abilities")), scales = "free") + 
  theme_few()+
  theme(legend.position = "none", 
        axis.title.x = element_text(size = 8), 
        axis.title.y = element_text(size = 8), 
        axis.text.x = element_text(size = 6), 
        axis.text.y = element_text(size = 6),
        strip.text.x = element_text(size = 8), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) + 
  xlab("Age (months)") + 
  ylab("Predicted Effect Size") 
  


p
```


```{r}
summarise_example_df <- categorized_age_pred_df %>% 
  filter(mean_age_months == 20) %>%
  filter(
    pred == min((categorized_age_pred_df %>% filter(mean_age_months == 20))$pred) | 
    pred == max((categorized_age_pred_df %>% filter(mean_age_months == 20))$pred)
  ) %>% 
  mutate(pred = round(pred, 2))

```




This current synthesis highlights the variation in developmental trajectories, challenging the traditional “milestone” view of cognitive development. Under the milestone view, learning and development are discrete and sequential: all infants would follow some developmental sequences and acquire skills in that order [@kuhl2004early; @wilks2010developmental]. Our findings suggest that this view is missing two important details. First, at any given age, psychological constructs could have a wide range of effect sizes. For example, at 20 months of age, the predicted effect sizes for communication skills range from `r filter(summarise_example_df, ds_name == "Switch task")$pred` (Switch task) to `r filter(summarise_example_df, ds_name == "Gaze following (combined)")$pred` (Gaze following). The differences between the strengths of the effect may reflect the differences in how these skills contribute to communication, with some playing a more significant role than others. In addition, the development of these skills could follow significantly different trajectories, with some increasing exponentially with age and others staying constant throughout early childhood. The heterogeneity of the developmental process calls for developing a more nuanced and integrated developmental theory. 


The heterogeneity can also partly be attributed to the wide variety of research methods. In the current analysis, we focused on in-lab experimental work, and thus the effect sizes may as well reflect how well the research methods capture the phenomenon of interest. Indeed, we have shown that subtle experimental procedure changes (e.g. stimuli exposure methods) could significantly alter the effect sizes. Moreover, methods’ impact varies across domains, with some domains being more susceptible to methodological factors than others. Finally, the developmental trajectories that we document could be influenced by researchers adapting their methods to participants of different ages. Our findings call attention to the importance of understanding methods’ nuances: rather than treating methods as a mirror perfectly reflecting the phenomenon, they should be regarded as an imperfect lens that could distort our perception of the phenomenon. 

```{r}
m_i2 = round(mean(i2_df$i2), 2) 
sd_i2 = round(sd(i2_df$i2),2) 

```


Of course, meta-analysis is not a perfect tool either. Despite the inclusion of a variety of moderators, we can explain relatively little variation in the datasets. One measure of heterogeneity is $I^2$, which calculates the proportion of variance accounted for by the meta-analytic model, relative to the total variance in the dataset. The mean $I^2$ across all the models we ran was `r m_i2` (*SD* : `r sd_i2`), indicating that the majority of the variation in effects across studies was unexplained by our moderators [@higgins2002quantifying]. 

Moreover, meta-analytic methods can often produce effect sizes significantly larger than a comparable large-scale replication [@kvarven2020comparing]. Part of the discrepancy can be attributed to the heterogeneity of research methods that is often minimized in a large-scale replication [@lewis2020puzzling]. While we have included methodological moderators in our analysis, it is highly likely that the coded moderators did not fully reflect the subtlety of research methods. However, the “Major author” effect found in many research domains could provide a window into understanding the subtler aspects of research methods. In the future, we could compare and contrast the methods and materials used by “major authors” and those by others. Doing so would allow us to pinpoint the differences and understand which aspects of the methods really matter, and which do not. 

Our ultimate goal is to offer a data-driven synthetic theory of cognitive development. Here we have made our first step toward that goal by offering a synthesis of meta-analyses across 23 different research domains. Moving forward, we aim to expand and refine our synthesis by including more research areas, correcting potential publication biases, and accounting for more detailed methodological factors. We would also like to make more connections between our meta-analysis-based work and the many ongoing analyses based on large-scale multi-site replication projects [e.g. ManyBabies: @frank2017collaborative]. Ultimately, we hope our analysis can provide a solid empirical foundation to help us better understand the complex and diverse processes involved in cognitive development. 

